Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-11 draft/accordionComplexSurfaces.tex
minor mistake picture

We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{McConville, PaluPilaudPlamondon} (see also~\cite{BrustleDouvilleMousavandThomasYildirim}).
We start with the kissing relation for walks.

>>>>

We can now define the non-kissing complex of a locally gentle bound quiver following~\cite{McConville, PaluPilaudPlamondon, BrustleDouvilleMousavandThomasYildirim}.
We start with the kissing relation for walks.
